### 2020-08-11 LaTeX/sections/paper.tex
SGX solution completed

\item \textbf{{Optimistic Rollups.}} In this scheme, assertions are assumed to be valid if there is no dispute posted about them with a certain window of time (a.k.a. "the challenge period'). Here, dispute resolution is a gas-costly method as the CallMarket contract would have to emulate the transaction on-chain to ensure the correctness the assertion. Also, assertions are publicly available and privacy of data is not protected. However, this does not affect our application as the new state only reflects the updated balances of traders and no secret is involved.

@@

%= = = = = =  = =  =  SGX=  = = = = = = = = =%
\item \textbf{{Using Intel SGX technology.}} Another solution pattern to close the market is to use SGX technology; a trusted execution environment~\cite{anati2013innovative}. In this method, the enclave can execute the \texttt{CloseMarket()} function offline and publishes an attestation Quote to the CallMarket contract. The contract then verifies the correctness of the Quote and if validated correctly, it transitions to the new state.

>>>>

\item \textbf{{Optimistic Rollups.}} In this scheme, assertions are assumed to be valid if there is no dispute posted about them with a certain window of time (a.k.a. "the challenge period'). Here, dispute resolution is a gas-costly method as the CallMarket contract would have to emulate the transaction on-chain to ensure the correctness the assertion. This scheme introduces a tradeoff between privacy and performance as all the assertions are publicly available and accessible. However, here the new state only reflects the updated balances of traders and no secret is involved.

@@

%= = = = = =  = =  =  SGX=  = = = = = = = = =%

\item \textbf{{Using Trusted Execution Environments.}} Another way of achieving execution of the \texttt{CloseMarket()} function is incorporating the Ethereum blockchain into the Trusted Execution Environments (TEEs) and decoupling the contract execution from consensus mechanism. TEEs enable secure execution of applications in an isolated processing environment called the \textit{enclave}. Here, the enclave could execute the \texttt{CloseMarket()} function off-chain in TEEs and publish an on-chain attestation Quote to the CallMarket contract. The contract then verifies the correctness of the Quote and if validated correctly, it transitions to the new state. Ekiden is an example that uses Intel SGX to solve the scalability and confidentiality issues with the smart contract execution~\cite{cheng2019ekiden}. A drawback of this scheme is in order to achieve confidentiality-preserving smart contracts we have to trust a trusted party in the form of the hardware manufacturer (\eg Intel).
